\documentclass[11pt, letterpaper]{article}

% Set the page margins
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}

\usepackage[utf8]{inputenc} % use UTF-8
\usepackage[colorlinks=false, allbordercolors={0 0 0},%
            pdfborderstyle={/S/U/W 1}]{hyperref} % links and stuff
\usepackage{multicol}
\usepackage{elements}
\usepackage{microtype}
\usepackage{enumitem}

% Fix sections
\usepackage[compact]{titlesec}
\renewcommand{\thesection}{}
\renewcommand{\thesubsection}{}
\titleformat{\section}[hang]%
    {\normalfont\bfseries\Large}{\vspace{3pt}}{-1pt}{\vspace{-3pt}}
\titleformat{\subsection}[hang]%
    {\normalfont\bfseries\large}{\vspace{3pt}}{-1pt}{\vspace{-5pt}}

% Format lists
\setlist{noitemsep, topsep=0pt}
\def\labelitemi{-}

% remove page numbers from the document
\pagestyle{empty}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\setlength{\columnsep}{20pt}

% Fix compilation bug with certain LaTeX versions
\usepackage{csquotes}
\MakeOuterQuote{"}
\let\textquotedbl="

\begin{document}

\input{header.tex}

%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\begin{multicols}{2}
\raggedcolumns
\textbf{Masters of Science, Computer Engineering} \\
\textit{At the University of Florida} \\
Currently enrolled in my first semester \\
Should graduate December 2015

\columnbreak

\textbf{Bachelors of Science, Computer Engineering} \\
\textit{At the University of Florida} \\
Graduated December 2014, with a 3.42 GPA
\end{multicols}

%% EMPLOYMENT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Employment}

\begin{multicols}{2}
\raggedcolumns
\textbf{Facebook Internship, \textit{Summer 2015}} \\
I have received and accepted an offer to work as a Front End Engineer Intern
at Facebook.

\columnbreak

\textbf{Amazon Internship, \textit{Summer 2014}} \\
I recently completed an internship with Amazon’s Fulfillment team in Seattle.
I declined a return offer in favor of Facebook.
\end{multicols}

\vfill

%% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Current Projects}

\datedsubsection{Honeybadger}{Spring 2015}

An extremely easy-to-use tool for configuring and running tor relays and full
bitcoind nodes. It uses a long list of technologies to automate installation,
upgrades, and error recovery, as well as to provide metrics.

The goal of the project is to assist these decentralized and trustless networks,
by encouraging people to run them on cheap and potentially unreliable hardware
or virtual machines.

\datedsubsection{Empress}{Fall 2015}

A lightweight email-focused fork of the popular configuration tool "Sovereign"
that makes it simple and inexpensive to run your own secure email server, and to
migrate from an existing IMAP server.

\vfill

\section{Past Projects}

\datedsubsection{IPOP (IP-over-P2P)}{Summer 2012}
A P2P VPN working by forwarding raw packets from a TAP device over UDP via
STUN and TURN using libjingle (part of WebRTC) and XMPP.

\begin{itemize}
    \item Raw packet networking with Linux
    \item Multiple routing modes (using a social graph or a fixed group)
    \item Cloud, mobile, and social applications
\end{itemize}%

\datedsubsection{iDigBio}{Summer 2012}

I wrote packaging scripts for a Python-based user-friendly upload tool. Targets
were:

\begin{itemize}
    \item Windows (via cx\_freeze)
    \item Mac OS X (via py2app)
    \item A Virtual Appliance (via VirtualBox and Puppet)
\end{itemize}

iDigBio is an NSF 10+ year project, so a strong emphasis was placed on
maintainability.

\pagebreak

\datedsubsection{NotVeryCleverBot}{Spring 2013}

A highly experimental AI commenting robot for the Reddit social network.

\begin{itemize}
    \item 26 stars and 6 forks on Github.
    \item Over 6,000 comment “karma” points on Reddit.
\end{itemize}

The bot was written quickly as a prototype in MongoDB, and has since been
partially re-written in CoffeeScript with MySQL.

\datedsubsection{Century}{Fall 2011 and Spring 2012}

I personally and independently developed library to automate various
web-resources operated by the University of Florida via screen-scraping.

\begin{itemize}
    \item Medium-to-large library, containing more than 10k LOC.
    \item Uses LXML to parse page content.
    \item Designed to be fault-tolerant.
\end{itemize}

\datedsubsection{Prelude.mk}{Fall 2013}

A fun proof-of-concept port of some of the more interesting bits of Haskell’s
prelude.hs to GNU make without shelling out or using guile. GNU make is a
Turing-complete functional language, but lacks many simple features, such basic
arithmetic.

\vfill\vfill\vfill\vfill

%% TECHNOLOGIES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\columnsep}{13pt}
\begin{multicols}{3}
\raggedcolumns

\newenvironment{technologylist}[1]{%
    \section{#1}
    \begin{minipage}{\columnwidth}
        \begin{small}
            \begin{itemize}%
}{%
            \end{itemize}
        \end{small}
    \end{minipage}
    \columnbreak%
}

\begin{technologylist}{Coding Languages}
    \item Python
    \item Coffeescript \& Javascript
    \item Java
    \item C and C++
    \item Haskell
    \item POSIX Shell
\end{technologylist}
\begin{technologylist}{Markup Languages}
    \item \LaTeX
    \item Markdown
    \item HTML5
    \item HAML
    \item CSS, SASS, \& LESS
    \item JSON \& YAML
\end{technologylist}
\begin{technologylist}{Technologies}
\item Debian GNU/Linux
\item Bash, Zsh, \& POSIX Shell
\item Vim
\item Git DVCS
\item Nginx
\item Postfix \& Dovecot
\item Ansible, Salt, \& Vagrant
\end{technologylist}

\end{multicols}

%% ENDNOTE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\simpleendnote{
    More projects, links, and fun facts at \url{http://benjam.info/}.
}
\end{document}
